Recovery completeness: <br> Analysis of Bauer et al. (unpublished) Field experiment

### 2022-11-21 R/model_recovery_markdown.Rmd
Update

---
title: "Successional distance to reference state: <br> Analysis of Bauer et al. (unpublished) Field experiment"
author: "Markus Bauer <br>"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: github_document
---

@@

Successional distance sensu https://doi.org/10.1111/1365-2664.13526

@@

```{r}
sites <- read_csv(
  here("data", "processed", "data_processed_sites_nmds.csv"),
  col_names = TRUE, na = c("na", "NA", ""),
  col_types = cols(
    .default = "?",
    id = "f",
    plot = "f",
    site = "f",
    exposition = col_factor(levels = c("north", "south",
                                       "other")),
    sand_ratio = "f",
    substrate_depth = col_factor(levels = c("30", "15")),
    target_type = col_factor(
      levels = c("hay_meadow", "dry_grassland", "other")
      ),
    seed_density = "f"
    )
  ) %>%
  filter(reference == "2018" | reference == "2019" | reference == "2020" |
           reference == "2021") %>%
  mutate(
    survey_year_fct = factor(survey_year),
    survey_year = as.numeric(survey_year),
    botanist_year = str_c(survey_year, botanist, sep = " "),
    n = recovery_time
    )
```

>>>>

---
title: "Recovery completeness: <br> Analysis of Bauer et al. (unpublished) Field experiment"
author: "Markus Bauer <br>"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: github_document
---

@@

Recovery completeness sensu Rydgren et al. (2018) https://doi.org/10.1111/1365-2664.13526

@@

```{r}
sites <- read_csv(
  here("data", "processed", "data_processed_sites_nmds.csv"),
  col_names = TRUE, na = c("na", "NA", ""),
  col_types = cols(
    .default = "?",
    id = "f",
    plot = "f",
    site = "f",
    exposition = col_factor(levels = c("north", "south",
                                       "other")),
    sand_ratio = "f",
    substrate_depth = col_factor(levels = c("30", "15")),
    target_type = col_factor(
      levels = c("hay_meadow", "dry_grassland", "other")
      ),
    seed_density = "f"
    )
  ) %>%
  filter(reference == "2018" | reference == "2019" | reference == "2020" |
           reference == "2021") %>%
  mutate(
    survey_year_fct = factor(survey_year),
    survey_year = as.numeric(survey_year),
    botanist_year = str_c(survey_year, botanist, sep = " "),
    n = recovery_completeness
    )
```
